---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# narSCIssus

<!-- badges: start -->
<!-- badges: end -->

The goal of narSCIssus is to help scientists to generate 'business cards' that can be shared in their personal websites and/or social media to showcase the impact of their research. To do so, narSCIssus uses data from Google Scholar to generate the text of the business card, and from PubMed to render a world map indicating countries where your current and pasts collaborators are based on.

## Installation

You can install the development version of narSCIssus from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Benjamin-Valderrama/narSCIssus")
```

## Example

Since narSCIssus uses information from PubMed, you can use advanced queries supported by [Entrez](https://www.ncbi.nlm.nih.gov/books/NBK3837/) to filter other researchers with your exact (or similar) name.

In this example, I use my name followed by the Mesh Term 'AU' and the keyword 'microbiome' to retrieve all PubMed publications where Benjamin Valderrama is listed as an author and contain the word microbiome.

```{r example1, fig.width=12, fig.height=7, fig.align='center', echo=TRUE}
library(narSCIssus)
make_business_card("Benjamin Valderrama[AU] microbiome")
```

However, simpler queries can be made. For instace, you could use just your name
```{r example2, fig.width=12, fig.height=7, fig.align='center', echo=TRUE}
library(narSCIssus)
make_business_card("Benjamin Valderrama")
```

Additionally, notice that by removing the keyword 'microbiome' from the second search, a paper published by the author Benjamin Valderrama that wasn't about the topic 'microbiome' was included. This examples shows that (similar but) different search terms may produce discrepant results, thus users should be use search terms with caution.

## Further development

I wrote narSCIssus during my holidays as an small experiment. However, I do want to add some features. I share my ideas here -mostly- to keep me accountable :joy:

* Make shiny app for narSCIssus
* Allow users to provide affiliations to narrow down ambiguous Google Scholar searches
* Add customization to the card. User-defined color for countries and font family and size
